---
title: "Getting Started Doc"
author: "Michael Sieler"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    number_sections: yes
    theme: united
    highlight: tango
  pdf_document: 
    toc: yes
    toc_depth: '3'
    
---

This is a template document to get you started. 

## Troubleshooting:
* Make sure you have all libraries installed, otherwise the loading functions will fail.
* Path names will fail if your `.Rproj` file is not located in the top level of you project repository
  * For example, it should be located here: `/Path_to_Project/ProjectName/<name_of_project>.Rproj`


## Setup environment

This chunk of code will need to be run prior to running any of the scripts in `Code/Analysis` directory.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)  # Sets default knit settings for document

# Check project file location is in correct directory
proj.path <- getwd()

# SourceFolder function
source(paste0(proj.path,"/Code/Functions/StartFunctions/sourceFolder.R"))

# Import all helper functions found in `/Functions`
sourceFolder(paste0(proj.path,"/Code/Functions/StartFunctions"), T)
sourceFolder(paste0(proj.path,"/Code/Functions/HelperFunctions"), T)



# Important Paths
path.code <- paste0(proj.path,"/Code")
path.data <- paste0(proj.path,"/Data")
path.objects <- paste0(proj.path, "/Data/R_objects")
path.input <- paste0(proj.path,"/Data/Input") 
path.results <- paste0(proj.path,"/Results") 

# Load Environment
## This loads all the data required for analysis.
# 
# load(file.path(path.data,
#                "R_objects/RoL_HeaterTrial_PostMicrobiomeProcessing_ENV_2024-02-21.RData"
#                ))


```


## Analyses

### Stats & Plots

Run this code to:
  - Calculate alpha diversity scores
  - Calculate beta dissimilarity matrices
  - Run code to generate alpha and beta stats and plots

```{r}
# This function will run all the scripts within the folders contained in Analysis directory
source(paste0(proj.path,"/MicrobiomeProcessing_2024-07-08.R"))

```

